Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-21 GEMDataSource.Rmd
Corrected link to new dataframe

@@

@@

library(stargazer)
stargazer(CompleteDataset, column.separate = TRUE, type = 'html')

>>>>

# Import GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is

SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)

@@

### Clean SupportiveTeaching

#

@@

library(stargazer)
stargazer(CompleteDataset, type = 'html')
